\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Armita Safa}
\address{\small{No. 17, 5th Golzar, Hejrat ST, Central Payambar ST,
Shahid Sattari HWY, Tehran, 1473644692}}
\address{(+98)~937~935~4595 \\ armt.safa@gmail.com}

\begin{document}

%-------------------------------------------------------------------------
%	EDUCATION
%-------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection} {University of Tehran}{2015 - present} {Bachelor of Science, Computer Engineering}{Current GPA: 17.62/20 (Ranked 2nd)}
\begin{itemize} \itemsep -2pt
    \item Significant courses(out of 20): Compiler Design(20), Data Transmission(20), Linear Control Systems(19.9), Hardware/Software Co-design(19.8), Wireless Networks(19.5), Computer Networks(19.1), Real-time Embedded Systems(18.5), Computer Architecture(17.95), Data Structures and Algorithms(17.7), Algorithmic Graph Theory(17.5)
    \item Final Year GPA: 19.72/20
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Farzanegan High School}{2011 - 2015}{Diploma, Mathematics and Physics Discipline}{GPA:19.93/20}
(Affiliated with the National Organization for Development of Exceptional Talents)
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------
%	RESEARCH EXPERIENCE
%-------------------------------------------------------------------------

\begin{rSection}{Research Experience}

\begin{rSubsection}{Undergraduate Research Assistant}{2018 - present}{Institute for Research in Fundamental Sciences (IPM)}{}
Supervised by Dr. Pooya Shariatpanahi; Working on applying Deep Learning techniques to the physical layer of network.
\end{rSubsection}

\begin{rSubsection}{Summer Research Intern}{Summer 2019}{Center of Bioinformatics, Saarland University\\Joint with Max Planck Institute for Informatics}{}
Supervised by Prof. Dr. Tobias Marschall; Worked on error correction for long noisy reads.
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------
%	TEACHING ASSISTANCE
%-------------------------------------------------------------------------

\begin{rSection}{Teaching ASSITANCE}

\begin{rSubsection}{}{}{}{}
\begin{itemize} \itemsep -6pt
\item \textbf{Head TA}, Data Transmission, Dr. Shariatpanahi \hfill Fall 2019
\item Discrete Mathematics, Dr. Mohammadi \hfill Spring 2018 - present
\item Computer Networks, Dr. Khonsari \hfill Fall 2018 - present
\item Programming Languages and Compilers, Dr. Hojjat \hfill Spring 2019
\item Introduction to Computing Systems and Programming, Dr. Moradi \hfill 2016 - 2017
\item Microprocessors, Dr. Fatemi \hfill Fall 2018
\item Electrical Circuits, Dr. Sadrossadat \hfill Fall 2017
\end{itemize}
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------
%	NOTABLE PROJECTS
%-------------------------------------------------------------------------

\begin{rSection}{Notable Projects}

\begin{rSubsection}{Sound-following Robot}{2019}{Real-time Embedded Systems Course}{}
{A real-time robot that follows a sound with a certain frequency in a noisy environment.}
\end{rSubsection}

\begin{rSubsection}{Smoola Compiler}{2018}{Compiler Design and Implementation Course}{}
{A compiler for a custom object-oriented language called Smoola; Smoola code compiled to Java bytecode.}
\end{rSubsection}

\begin{rSubsection}{Floodlight Extension}{2018}{Computer Networks Course}{}
{Designed and implemented an algorithm for detecting the topology of a network and routing packets; Used Floodlight OpenFlow Controller.}
\end{rSubsection}

\begin{rSubsection}{ACM Vahed}{2017}{}{}
{Worked as a part of ACM Vahed team, a utility to help University of Tehran students choose courses for each semester; developed with Ruby on Rails.}
\end{rSubsection}

\begin{rSubsection}{Pintos Scheduler}{2017}{Operating Systems Course}{}
{A customized scheduler for Pintos that schedules processes based on IO usage, resulting in increased efficiency.}
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------
%	HONORS AND AWARDS
%-------------------------------------------------------------------------

\begin{rSection}{Honors and Awards} 
\begin{itemize}
    \item FOE (Faculty of Engineering) award for ranking {\bf3$^{rd}$} among computer engineering students \hfill 2018
    \\ \textit{University of Tehran}
    \item Ranked {\bf202$^{nd}$} in Iranian University Entrance Exam (Top \%0.3)\hfill 2015
    \\ \textit{Mathematics and Physics Discipline}
\end{itemize}
\end{rSection}

%-------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE
%-------------------------------------------------------------------------

\begin{rSection}{Professional Experience}

\begin{rSubsection}{Digikala}{Jun 2018 - Sep 2018}{Software Engineer at Digipay}{}
\item Member of Digipay team; aiming to provide secure e-payment services.
\item Worked on design and implementation of algorithms for Smart IPG Routing service.
\item Developed with Java Spring.
\end{rSubsection}

\end{rSection}


%-------------------------------------------------------------------------
%	EXTRA-CURRICULAR
%-------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular} \itemsep -4pt

\begin{rSubsection}{Online Courses}{}{}{}
\itemsep0em 
\begin{itemize}
    \item Bioinformatics Specialization, University of California San Diego
    \item Algorithms for DNA Sequencing, Johns Hopkins University
    \item Advanced Bioinformatics, Sharif University of Technology
\end{itemize}
\end{rSubsection}

\begin{rSubsection}{Position of Responsibility}{}{}{}
\begin{itemize}
    \item Membership Chairperson \hfill {2016 - 2017}
    \\ {University of Tehran ACM Student Chapter}
    \\ \textit{(ACM is widely recognized as the premier membership organization for computing professionals, delivering resources that advance computing as a science and a profession.)}
\end{itemize}
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------
%	SKILLS
%-------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C/C++, Python, Java; Familiar with MATLAB, R \\
Technologies \& Tools & Spring Framework, Git, HTML, CSS, Databases, \LaTeX \\
Simulation \& Synthesis & Verilog, Modelsim, Multisim, HSpice, Quartus, ISE \\
Languages & English\textit{(Fluent)}, German\textit{(Elementary)}, Farsi\textit{(Native)}
\end{tabular}

\end{rSection}



\end{document}
